### 2024-03-25 doc/sections/introduction.tex
Gave it a shot

For MAV, we cannot use the phase space model, due to the presence of the self-dual connective.
\wen{%
      I think we can't quite say we \emph{cannot} use phase spaces, only that they do not immediately generalise to accommodate self-dual connectives, right?}
\bob{I think we can say ``The Phase Space proof of cut-elimination does not easily extend to the kind of self-dual connective present in BV and its extensions.'' Maybe elaborate by saying that the phase space model defines duality by means of a double negation with respect to one one of the monoidal structures, and ignores the other one completely. So I think it is unlikely that phase spaces can be adapted to BV.}

>>>>

The phase semantic proof of cut-elimination does not easily extend to include the kind of self-dual connective present in BV and its extensions.
The phase space model defines duals by means of double negation with respect to the monoidal structure, which means that attempts to extend the model with the self-dual non-commutative connective result in two distinct dual connectives, reminiscent of the non-commutative tensor and par introduced by Slavnov~\cite{Slavnov19:scmll}.
\wen{%
      I think we can't quite say we \emph{cannot} use phase spaces, only that they do not immediately generalise to accommodate self-dual connectives, right?}
\bob{%
      I think we can say ``The Phase Space proof of cut-elimination does not easily extend to the kind of self-dual connective present in BV and its extensions.'' Maybe elaborate by saying that the phase space model defines duality by means of a double negation with respect to one one of the monoidal structures, and ignores the other one completely. So I think it is unlikely that phase spaces can be adapted to BV.}
\wen{%
      Gave it a shot.}
